Abstractions and exemplars: the measure noun phrase alternation in German

### 2017-12-31 Latex/article.tex
Proofread acknowledgements, Sec 1.

\begin{acknowledgement}
  I thank (in alphabetical order) Felix Bildhauer, Susanne Flach, Elizabeth Pankratz, Samuel Reichert, Ulrike Sayatz, and Christian Zimmer for valuable discussions and comments.
  Also, I would like to thank the reviewers for Cognitive Linguistics as well as associate editor Dagmar Divjak for insightful comments which helped to improve the quality of this paper a lot.
  Furthermore, I thank Ulrike Sayatz for helping me to recruit the participants for the experiments.
  Elizabeth Pankratz thankfully also fixed my English.
  Finally, I am grateful to my student assistants Kim Maser for her work on the annotation of the concordances and Luise Rißmann for supervising most of the experiments.
  The research presented here was made possible in part through funding from the \textit{Deutsche Forschungsgemeinschaft} (DFG, personal grant SCHA1916/1-1).
\end{acknowledgement}

>>>>

\begin{acknowledgement}
  I thank (in alphabetical order) Felix Bildhauer, Susanne Flach, Elizabeth Pankratz, Samuel Reichert, Ulrike Sayatz, and Christian Zimmer for valuable discussions and comments.
  Also, I would like to thank the reviewers for Cognitive Linguistics as well as associate editor Dagmar Divjak for insightful comments which helped to improve the quality of this paper significantly.
  Furthermore, I thank Ulrike Sayatz for helping me to recruit the participants for the experiments.
  Elizabeth Pankratz thankfully also fixed my English.
  Finally, I am grateful to my student assistants Kim Maser, for her work on the annotation of the concordances, and Luise Rißmann, for supervising most of the experiments.
  The research presented here was made possible in part through funding from the \textit{Deutsche Forschungsgemeinschaft} (DFG, personal grant SCHA1916/1-1).
\end{acknowledgement}

### 2017-12-31 Latex/sections/1intro.tex
Proofread acknowledgements, Sec 1.

This paper deals with a morpho-syntactic alternation between two constructions that occurs only in a very specific type of measure noun phrase in German.
By \textit{alternation} I refer to a situation where two or more forms or constructions are available with no clear difference in acceptability, function, or meaning.
The study of lexical and constructional alternations has a long history in cognitively oriented corpus linguistics (for example, \citealp{BresnanEa2007,BresnanHay2010,BresnanFord2010,DivjakArppe2013,Gries2015,NessetJanda2010,Wulff2003}).
This area of research is based on the assumption that language is a probabilistic phenomenon \citep{Bresnan2007} where alternants are chosen neither deterministically nor fully at random.
Instead, multifactorial models are constructed which incorporate influencing factors from diverse levels, including contextual factors.
The estimation of the model coefficients quantifies the influence that the factors have on the probability that either alternant is chosen.
There are two fundamental issues to consider with respect to this tradition as a part of cognitive linguistics in the broad sense.
First, there is the question of whether corpus data do provide any insight into cognitive representations at all.
This question can and should be answered by testing how well corpus-derived models converge with or diverge from experimental findings, which provide more direct evidence of mental representations and processes but are often intrinsically narrower in scope.
Second and much related to the first question, the appropriate modelling of such results in cognitive linguistics is a key issue.

As for the first point, there has for a long time been an interest in correlating probabilistic generalisations extracted from corpus data with results from experimental work (for example, \citealp{ArppeJaervikivi2007,BresnanEa2007,BresnanFord2010,DivjakGries2008,DivjakEa2016,FordBresnan2013}).
This is often called a \textit{validation} of the corpus-derived findings, but \citet[303]{Divjak2016a} criticises this choice of words ``because it creates the impression that behavioral experimental data is inherently more valuable than textual data,'' citing \cite{TummersEa2005}, who state that a corpus is ``a sample of spontaneous language use that is (generally) realized by native speakers''.
See also \citet{Newman2011} for a very positive view of corpora as a source of data in cognitive linguistics in their own right.
However, as \citet[486--487]{Dabrowska2016} convincingly argues, this does not imply that we can in some way ``deduce mental representations from patterns of use,'' \ie\ from corpus data.%
\footnote{Epistemologically, I think she refers to acts of \textit{induction} rather than \textit{deduction}.}
It would be highly surprising if this were possible, and the same holds for experimental methods, albeit to a different degree.
Nobody assumes that we can inductively infer mental representations from experiments, which -- as opposed to corpus studies -- even allow for direct access to the cognitive agent and offer much better possibilities to control experimental conditions and nuisance variables.
Rather, under the standard approach, a theory of cognitive representation is pre-specified.
Then, predictions are derived from this theory \textit{before} the experiment or the corpus study is conducted in order to \textit{test} the theory.
While the same approach is by and large applicable to corpus data, I now discuss some relevant differences.

As mentioned above, the central question is whether usage data as found in corpora are truly predictive of speakers' and writers' cognitive representation of language and\slash or of their overall linguistic behaviour; and this is where the experimental validation (or, more neutrally \textit{corroboration}) comes into play.
An overview of this issue was given by \cite{NewmanSorensenduncan2015}, who enumerate a number of studies which show how corpus data and experimental data converge (such as \citealp{BresnanEa2007,DurrantDoherty2010,GriesWulff2005,GriesEa2005}) and a number of studies where the two types of data did not lead to diverging or only partially converging results (such as \citealp{ArppeJaervikivi2007,Dabrowska2014,Mollin2009}).
When researchers do not achieve convergence, they mostly try to explain this by differentiating between the actual cognitive construct and what the pooled usage data as found in corpora represent, for example \citet[411]{Dabrowska2014}, who lists a long number of possible reasons to explain why subjects in her experiment diverged in their word association preferences from collocation measures extracted from corpora.
In some cases, researchers simply argue for a more adequate statistical analysis to increase the fit between corpus data and subjects' reactions in experiments, for example \cite{DivjakEa2016}, who show that generalised additive models (GAMs) are better suited than generalised linear models (GLMs) in the analysis of their reading-time experiment based on data extracted from previous corpus studies.
Much more optimistically compared to these publications dealing with possible frictions between usage and experimental data, \cite{StefanowitschFlach2016} recently proposed a straightforward positivist perspective of corpora as representing the input of an average adult speaker, thus licensing inferences from corpus data to cognitive representations learned from such data under a ``corpus-as-input'' view.
They state that ``in this wider context, large, register-mixed corpora such as the British National Corpus [\ldots] may not be perfect models of the linguistic experience of adult speakers, but they are reasonably close to the input of an idealized average member of the relevant speech community'' \citep[104]{StefanowitschFlach2016}.%
\footnote{This, of course, raises the old question of how corpora should be composed to represent what they are intended to represent.
As points of reference for determining ``representativeness'', at least three major criteria have been used, namely the distribution of texts or text types in the output of all speakers of a language (production-based), the distribution of the relevance of texts or text types in the whole speech community (relevance-based), and the distribution of speakers' exposure to different texts or text types (perception-based).
See \citet{Biber1993}, \citet{MceneryEa2006}, \citet{Leech2007}, \citet{Hunston2008} for overviews from different perspectives.}
In essence, this would entail that any generalisation extracted from the BNC can be attributed with some kind of mental reality.

Obviously, no clear picture has emerged yet, which is not surprising given the vast number of cognitive constructs assumed at diverse levels (such as the level of words in collocation research and much more complex constructional levels in alternation research involving lexical, syntagmatic, and contextual factors), the problems of corpus composition, the operationalisations involved in making experiments, and in the choice of statistical tools.
While far from providing definitive solutions, my discussion in Section~\ref{sec:conclusion} will provide possible explanations for the goodness of fit between the corpus data and the experimental data reported in Sections~\ref{sec:corpusstudies} and~\ref{sec:experimental}, much in the spirit of \citet{Dabrowska2014}.

I now turn to the second issue, namely which type of cognitive representation research on alternations provides evidence for.
The typical approach in alternation research is to annotate a large number of corpus sentences with linguistic features and to model the probability of the variants being chosen given these features.
The idea is that a variant is chosen when the influencing features cumulatively assume \textit{prototypical} values for that variant.
I other words, a variant of prototype theory with features \citep{Rosch1978} suggests itself, and some researchers such as \cite{Gries2003}, \cite{NessetJanda2010}, or \cite{Schaefer2016c} indeed commit to prototype theory in alternation modelling.
Under prototype theory, category membership is defined by similarity to an ideal exemplar, which is usually identified with characterising features (see \citealp{Taylor2008} for an overview).
While prototype theory is well suited for modeling constructional choices, it is just one of at least two major similarity-based theories of classification, the most prominent other framework being exemplar theory (\citealp{MedinSchaffer1978,Hintzman1986}).
Prototype theory and exemplar theory model essentially the same types of effects but differ significantly in whether they assume higher-level abstractions in the form of single maximally prototypical exemplars or their features (prototype theory) or assume that categories emerge through the storage of many exemplars and similarity classification on those exemplars (exemplar theory).
Similarity-based categorisation is seen as the central and conceptually sufficient approach to linguistic categorisation by many cognitive linguists; see for example \cite{Taylor2003} for a comprehensive treatment in terms of prototype theory.
In the influential framework of cognitive grammar \citep{Langacker1987}, prototypes (which, as should be remembered, represent abstractions already in cognitive science) are literally taken as prototypical exemplars, and there is an additional level of fully discrete abstractions in the form of schemas.
Schemas are characterised by the properties common to all members of the category, whereas a prototypical category member might have very specific additional properties not at all shared by all or even most members \citep[371-375]{Langacker1987}.
The prototype can serve as a reference point when classifying new objects which do not share all properties of the schema, but this would (if repeated) lead to the creation of an even more abstract (hierarchically higher and less specific) schema which describes the new member and the ones belonging to the previous schema.
As pointed out by \citet[136--137]{Langacker1987}, schemas and prototypes thus fulfil different roles and can be assumed to co-exist.
A strict exemplar view of language is incompatible, as far as I can see, with Langacker's view of schemas, but any theory of categorisation that allows for at least some kind of abstraction, is not in principled contradiction with it.%
\footnote{See especially theories with varying intermediate levels of abstraction described below, which seem compatible with Langacker's formation of schema hierarchies through classification by prototype similarity.}
In the remainder of this paper, I do not use schemas in my descriptions of the relevant categories, mostly because the aspect of similarity and fuzzy classification is central to my point, and a formulation in terms of schemas would bring about an unnecessarily high degree of abstraction (see \citealp[70--71]{Taylor2003} for a parallel argument).
However, I fully describe the abstract features of the prototypes, of course, while accounting for item-specific and exemplar effects.

Turning back to the prototype vs.\ schema debate, \cite{Barsalou1990} already showed that prototype and exemplar theory model the same types of effects and are informationally equivalent.
Consequently, experiments which favour one theory over the other use procedural behaviour of subjects in experiments, for example the speed of category retrieval, as opposed to mere output data.
In very early experiments, \cite{PosnerKeele1968} showed, for example, that highly prototypical unseen exemplars were categorised more easily by subjects compared to less prototypical ones which had been included in the learning data.
This was (at the time) taken as evidence that subjects categorise by prototypes.%
\footnote{See \citet{StormsEa2000} for a comparison of the theories in different experimental settings.}
Since corpus data only show artefacts of production events and we have no experimental access to the speaker's or writer's performance and their actual similarity judgements, one should be sceptical whether corpus analysis alone could ever decide which theory of mental representation is more suitable (see also \citealp[22]{Gries2003} and the \citealp[486--487]{Dabrowska2016} quote above).

@@

On the other hand, the trade-off one has to accept when doing experiments with highly simplified stimuli and very simple tasks is their lack of \textit{external validity} (\ie their generalisability) and their high dependence on potentially problematic operationalisations of constructs, control of confounding factors in the face of a limited number of available subjects, etc. (in other words, critical dependence on \textit{construct validity} and \textit{internal validity}).%
\footnote{An accessible overview of the different types of validity can be found in Chapter~1 of \citet{MaxwellDelaney2004}.}
Tasks in cognitive science have been criticised exactly for their lack of external validity, for example by \citet{Murphy2003}.
From a linguistic perspective, it is remarkable in this context that \cite{VoorspoelsEa2011} consider their experimental task -- which is the assignment of typicality scores to nouns from the domains of \textit{animals} and \textit{artefacts} to categories like \textit{bird}, \textit{fish}, \textit{clothing}, or \textit{tools} -- a study of ``superordinate natural language categories, whereas most evidence supporting exemplar representations has been found in artificial categories of a more subordinate level'' \citep[1013]{VoorspoelsEa2011}.
Corpus linguists interested in probabilistic alternation modelling deal with much more complex high-level categories and use large and complex feature sets, especially in (morpho-)syntax.%
\footnote{Notice, however, that recently, approaches have emerged which solve at least some problems by abandoning linguistic high-level features altogether \citep{BaayenEa2016,RamscarPort2016}.
Clearly, they have not (or at least not yet) reached mainstream popularity, and it remains to be seen how well they perform on a broader range of questions.}
It is thus an advantage of much linguistic work on categorisation that it deals with complex and realistically produced data, because this greatly improves the external validity of studies.
An ideal contribution to the research on (levels of) category abstraction in the human mind by cognitive corpus linguists is thus if we provide analyses which have great external validity and complexity while carefully making sure whether and to which degree these finding correlate with reactions from cognitive agents under more controlled experimental conditions.

>>>>

\hl{This paper deals with a morpho-syntactic alternation between two constructions that occurs only in a very specific type of measure noun phrase in German.}
By \textit{alternation} I refer to a situation where two or more forms or constructions are available with no clear difference in acceptability, function, or meaning.
The study of lexical and constructional alternations has a long history in cognitively oriented corpus linguistics (for example, \citealp{BresnanEa2007,BresnanHay2010,BresnanFord2010,DivjakArppe2013,Gries2015,NessetJanda2010,Wulff2003}).
This area of research is based on the assumption that language is a probabilistic phenomenon \citep{Bresnan2007} where alternants are chosen neither deterministically nor fully at random.
Instead, multifactorial models are constructed which incorporate influencing factors from diverse levels, including contextual factors.
The estimation of the model coefficients quantifies the influence that the factors have on the probability that either alternant is chosen.
There are two fundamental issues to consider with respect to this tradition as a part of cognitive linguistics in the broad sense.
First, there is the question of whether corpus data do provide any insight into cognitive representations at all.
This question can and should be answered by testing how well corpus-derived models converge with or diverge from experimental findings, which provide more direct evidence of mental representations and processes but are often intrinsically narrower in scope.
Second and closely related to the first question, the appropriate modelling of such results in cognitive linguistics is a key issue.

Concerning the first point, there has for a long time been an interest in correlating probabilistic generalisations extracted from corpus data with results from experimental work (for example, \citealp{ArppeJaervikivi2007,BresnanEa2007,BresnanFord2010,DivjakGries2008,DivjakEa2016,FordBresnan2013}).
This is often called a \textit{validation} of the corpus-derived findings, but \citet[303]{Divjak2016a} criticises this choice of words ``because it creates the impression that behavioral experimental data is inherently more valuable than textual data,'' citing \cite{TummersEa2005}, who state that a corpus is ``a sample of spontaneous language use that is (generally) realized by native speakers''.
See also \citet{Newman2011} for a very positive view of corpora as a source of data in cognitive linguistics in their own right.
However, as \citet[486--487]{Dabrowska2016} convincingly argues, this does not mean that we can in some way ``deduce mental representations from patterns of use,'' \ie\ from corpus data.%
\footnote{Epistemologically, I believe she refers to acts of \textit{induction} rather than \textit{deduction}.}
It would be highly surprising if this were possible, and the same holds for experimental methods, albeit to a different degree.
Nobody assumes that we can inductively infer mental representations from experiments, which -- as opposed to corpus studies -- even allow for direct access to the cognitive agent and offer much better possibilities to control experimental conditions and nuisance variables.
Rather, under the standard approach, a theory of cognitive representation is pre-specified.
Then, predictions are derived from this theory \textit{before} the experiment or the corpus study is conducted in order to \textit{test} the theory.
While the same approach is by and large applicable to corpus data, I now discuss some relevant differences.

As mentioned above, the central question is whether usage data as found in corpora are truly predictive of speakers' and writers' cognitive representation of language and\slash or of their overall linguistic behaviour; and this is where the experimental validation (or, more neutrally, \textit{corroboration}) comes into play.
An overview of this issue was given by \cite{NewmanSorensenduncan2015}, who enumerate a number of studies which show how corpus data and experimental data converge (such as \citealp{BresnanEa2007,DurrantDoherty2010,GriesWulff2005,GriesEa2005}) and a number of studies where the two types of data \hl{did not lead to diverging} or only partially converging results (such as \citealp{ArppeJaervikivi2007,Dabrowska2014,Mollin2009}).% converge = did not diverge. What do you mean by the second point?
When researchers do not achieve convergence, they mostly try to explain this by differentiating between the actual cognitive construct and what the pooled usage data as found in corpora represent, for example \citet[411]{Dabrowska2014}, who lists a long number of possible reasons to explain why subjects in her experiment diverged in their word association preferences from collocation measures extracted from corpora.
In some cases, researchers simply argue for a more adequate statistical analysis to increase the fit between corpus data and subjects' reactions in experiments, for example \cite{DivjakEa2016}, who show that generalised additive models (GAMs) are better suited than generalised linear models (GLMs) in the analysis of their reading-time experiment based on data extracted from previous corpus studies.
Much more optimistically compared to these publications dealing with possible frictions between usage and experimental data, \cite{StefanowitschFlach2016} recently proposed a straightforward positivist perspective of corpora as representing the input of an average adult speaker, thus licensing inferences from corpus data to cognitive representations learned from such data under a ``corpus-as-input'' view.
They state that ``in this wider context, large, register-mixed corpora such as the British National Corpus [\ldots] may not be perfect models of the linguistic experience of adult speakers, but they are reasonably close to the input of an idealized average member of the relevant speech community'' \citep[104]{StefanowitschFlach2016}.%
\footnote{This, of course, raises the old question of how corpora should be composed to represent what they are intended to represent.
As points of reference for determining ``representativeness'', at least three major criteria have been used, namely the distribution of texts or text types in the output of all speakers of a language (production-based), the distribution of the relevance of texts or text types in the whole speech community (relevance-based), and the distribution of speakers' exposure to different texts or text types (perception-based).
See \citet{Biber1993}, \citet{MceneryEa2006}, \citet{Leech2007}, \citet{Hunston2008} for overviews from different perspectives.}
In essence, this would entail that any generalisation extracted from the BNC can be attributed \hl{with (to?)} some kind of mental reality. % "attributed with" doesn't mean anything. What do you mean to say here?

Obviously, no clear picture has emerged yet, which is not surprising given the vast number of cognitive constructs assumed at diverse levels (such as the level of words in collocation research and much more complex constructional levels in alternation research involving lexical, syntagmatic, and contextual factors), the problems of corpus composition, \hl{the operationalisations involved in making experiments, and in the choice of statistical tools.} % Is the highlighted bit one coordinated unit? i.e. operationalisations involved in making experiments and choice of statistical tools? Then: "...the problems of corpus composition, and the operationalisations involved in making experiments and in the choice...". If not, take out the "in" fom "in the choice of statistical tools" and leave everything else the same.
While far from providing definitive solutions, my discussion in Section~\ref{sec:conclusion} will provide possible explanations for the goodness of fit between the corpus data and the experimental data reported in Sections~\ref{sec:corpusstudies} and~\ref{sec:experimental}, much in the spirit of \citet{Dabrowska2014}.

I now turn to the second issue, namely which type of cognitive representation research on alternations provides evidence for.
The typical approach in alternation research is to annotate a large number of corpus sentences with linguistic features and to model the probability of the variants being chosen given these features.
The idea is that a variant is chosen when the influencing features cumulatively assume \textit{prototypical} values for that variant.
In other words, a variant of prototype theory with features \citep{Rosch1978} could be applied, and some researchers such as \cite{Gries2003}, \cite{NessetJanda2010}, or \cite{Schaefer2016c} indeed commit to prototype theory in alternation modelling.
Under prototype theory, category membership is defined by similarity to an ideal exemplar, which is usually identified with characterising features (see \citealp{Taylor2008} for an overview).
While prototype theory is well suited for modeling constructional choices, it is just one of at least two major similarity-based theories of classification, the most prominent other framework being exemplar theory (\citealp{MedinSchaffer1978,Hintzman1986}).
Prototype theory and exemplar theory model essentially the same types of effects but differ significantly in whether they assume higher-level abstractions in the form of single maximally prototypical exemplars or their features (prototype theory) or assume that categories emerge through the storage of many exemplars and similarity classification on those exemplars (exemplar theory).
Similarity-based categorisation is seen as the central and conceptually sufficient approach to linguistic categorisation by many cognitive linguists; see for example \cite{Taylor2003} for a comprehensive treatment in terms of prototype theory.
In the influential framework of cognitive grammar \citep{Langacker1987}, prototypes (which, as should be remembered, represent abstractions already in cognitive science) are literally taken as prototypical exemplars, and there is an additional level of fully discrete abstractions in the form of schemas.
Schemas are characterised by the properties common to all members of the category, whereas a prototypical category member might have very specific additional properties not at all shared by all or even most members \citep[371-375]{Langacker1987}.
The prototype can serve as a reference point when classifying new objects which do not share all properties of the schema, but this would (if repeated) lead to the creation of an even more abstract (hierarchically higher and less specific) schema which describes the new member and the ones belonging to the previous schema.
As pointed out by \citet[136--137]{Langacker1987}, schemas and prototypes thus fulfil different roles and can be assumed to co-exist.
A strict exemplar view of language is incompatible, as far as I can see, with Langacker's view of schemas, but any theory of categorisation that allows for at least some kind of abstraction, is not in principled contradiction with it.%
\footnote{See especially theories with varying intermediate levels of abstraction described below, which seem compatible with Langacker's formation of schema hierarchies through classification by prototype similarity.}
In the remainder of this paper, I do not use schemas in my descriptions of the relevant categories, mostly because the aspect of similarity and fuzzy classification is central to my point, and a formulation in terms of schemas would bring about an unnecessarily high degree of abstraction (see \citealp[70--71]{Taylor2003} for a parallel argument).
However, I fully describe the abstract features of the prototypes, of course, while accounting for item-specific and exemplar effects.

Turning back to the prototype vs.\ \hl{schema} debate, \cite{Barsalou1990} already showed that prototype and exemplar theory model the same types of effects and are informationally equivalent. % Shouldn't this be prototype vs. exemplar? Since schemas are Langacker's thing and you don't mention them in this paragraph, but instead talk about exemplars?
Consequently, experiments which favour one theory over the other use procedural behaviour of subjects in experiments, for example the speed of category retrieval, as opposed to mere output data.
In very early experiments, \cite{PosnerKeele1968} showed, for example, that highly prototypical unseen exemplars were categorised more easily by subjects compared to less prototypical ones which had been included in the learning data.
This was (at the time) taken as evidence that subjects categorise by prototypes.%
\footnote{See \citet{StormsEa2000} for a comparison of the theories in different experimental settings.}
Since corpus data only show artefacts of production events and we have no experimental access to the speaker's or writer's performance and their actual similarity judgements, one should be sceptical whether corpus analysis alone could ever decide which theory of mental representation is more suitable (see also \citealp[22]{Gries2003} and the \citealp[486--487]{Dabrowska2016} quote above).

@@

On the other hand, the trade-off one has to accept when doing experiments with highly simplified stimuli and very simple tasks is their lack of \textit{external validity} (\ie their generalisability) and their high dependence on potentially problematic operationalisations of constructs, control of confounding factors in the face of a limited number of available subjects, etc. (in other words, critical dependence on \textit{construct validity} and \textit{internal validity}).%
\footnote{An accessible overview of the different types of validity can be found in Chapter~1 of \citet{MaxwellDelaney2004}.}
Tasks in cognitive science have been criticised exactly for their lack of external validity, for example by \citet{Murphy2003}.
From a linguistic perspective, it is remarkable in this context that \cite{VoorspoelsEa2011} consider their experimental task -- which is the assignment of typicality scores to nouns from the domains of \textit{animals} and \textit{artefacts} to categories like \textit{bird}, \textit{fish}, \textit{clothing}, or \textit{tools} -- a study of ``superordinate natural language categories, whereas most evidence supporting exemplar representations has been found in artificial categories of a more subordinate level'' \citep[1013]{VoorspoelsEa2011}.
Corpus linguists interested in probabilistic alternation modelling deal with much more complex high-level categories and use large and complex feature sets, especially in (morpho-)syntax.%
\footnote{Notice, however, that recently, approaches have emerged which solve at least some problems by abandoning linguistic high-level features altogether \citep{BaayenEa2016,RamscarPort2016}.
Clearly, they have not (or at least not yet) reached mainstream popularity, and it remains to be seen how well they perform on a broader range of questions.}
It is thus an advantage of much linguistic work on categorisation that it deals with complex and realistically produced data, because this greatly improves the external validity of studies.
An ideal contribution by cognitive corpus linguists to the research on (levels of) category abstraction in the human mind would thus be to provide analyses which have great external validity and complexity while carefully making sure that (and determining to what extent) these finding correlate with reactions from cognitive agents under more controlled experimental conditions.
